\section{Analysis}\label{sec:analysis}

Section~\ref{sec:requirements} introduced a set of requirements to judge the
results of this work and Section~\ref{sec:objectives} introduced a set of
objectives this research targeted for completion. This section reviews those
sections in the context of test results produced for this work.

% This work, by virtue of building on an Internet-based network, is accepting
% risks which make any consideration or application of its results inappropriate
% for use in large-scale high-risk elections. Specifically, the intrinsically
% electronic and remote properties, which are inherent in all publicly-available
% ``off-the-shelf'' blockchain technologies, present so large an attack surface
% for would-be attackers that it becomes an untenable foundation for any voting
% systems being considered for use in elections where a high-risk threat model is
% maintained. Correctness, security, integrity, verifiability, and efficacy are
% the primary concerns of the systems designed and considered in this research;
% however, it is worth noting that the privacy constraints offered by traditional
% voting systems are severely loosened within the scope of this research: no
% notion of receipt-freedom is assumed and privacy is only guaranteed insofar as
% the pseudo-anonymity provided by the Ethereum blockchain is
% maintained.\footnotemark{}
%
% \footnotetext{
%   It is feasible that blockchain technologies could demonstrate utility in
%   large-scale voting systems if incorporated using well-established and
%   known-safe patterns: e.g., voter verifiable paper audit trails, private
%   networks, requiring transactions be signed by authorized sources, using voting
%   machines which have been certified by a federal commission, which are being
%   hosted in traditional polling locations, and are leveraging the appropriate
%   cryptographic techniques to ensure privacy; e.g., homomorphic encryption,
%   blind signing, and mix networks.
%
%   % The feasibility of leveraging fully- or partially-decentralized blockchains
%   % as a foundation for large-scale voting systems demands significantly more
%   % research into crypto-economic incentivization and disincentivization models
%   % for honest and dishonest actors.
%
%   % That said, the computational and storage requirements of such a project
%   % would almost certainly necessitate a dedicated blockchain solution.
% }

\subsection{Requirements}
Table~\ref{tab:research-requirements-fulfilled} highlights these requirements
targeted from Section~\ref{sec:requirements} and provides an overview of what
was and was not fulfilled. \\

\begin{spacing}{1.1}
  \begin{longtabu} to \textwidth{X[0.1,l] X[2.3,j] X[0.8,c] X[0.8,c] X[0.8,c] X[1.1,c]}
    % \multicolumn{2}{c}{Requirements} \\
    \caption{Requirements targeted for fulfillment.} \\
    \toprule
    \multicolumn{2}{l}{{Requirements}}                                       & \multicolumn{3}{c}{Fulfilled}                  & {Unfulfilled} \\
                                                                               \cmidrule{3-5}
    \multicolumn{2}{l}{}                                                     & {Fully}       & {Mostly}       & {Partially}   &               \\
    \midrule
    \endhead
    \multicolumn{2}{l}{\emph{Technical}} \\
    % \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-6}
    % \cline{1-2}
    % \midrule
    % \multirow{10}{*}{\rot[90]{Technical}}     & Authentication               & \textbullet{} &                &               &               \\
                                              & Authentication               &               & \textbullet{}  &               &               \\
                                              & System Operational           & \textbullet{} &                &               &               \\
                                              & Reliability                  &               & \textbullet{}  &               &               \\
                                              & Security                     &               & \textbullet{}  &               &               \\
                                              & Auditing                     &               & \textbullet{}  &               &               \\
                                              & Functional                   &               & \textbullet{}  &               &               \\
                                              & Interoperability             &               &                & \textbullet{} &               \\
                                              & Certification                &               &                & \textbullet{} &               \\
                                              & Accessibility                &               &                &               & \textbullet{} \\
                                              & Usability                    &               &                &               & \textbullet{} \\
    % \midrule
    % \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-6}
    \addlinespace[0.4ex]
    \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-6}
    \multicolumn{2}{l}{\emph{Non-Functional}} \\
    % \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-6}
    % \cline{1-2}
    % \cmidrule{1-2}
    % \midrule
    % \multirow{5}{*}{\rot[90]{Non-Functional}} & Maintenance/Evolvability     &               & \textbullet{}  &               &               \\
                                              & Maintenance/Evolvability     &               &                & \textbullet{} &               \\
                                              & Assurance                    &               &                & \textbullet{} &               \\
                                              & Operational                  &               &                &               & \textbullet{} \\
                                              & Procedural                   &               &                &               & \textbullet{} \\
                                              & Legal                        &               &                &               & \textbullet{} \\
    \bottomrule\label{tab:research-requirements-fulfilled}
  \end{longtabu}
\end{spacing}

\subsubsection{Technical Requirements}
The technical requirements are ones which are meant to be fulfilled through the
design and architecture of the system. The system operational requirements are
considered fulfilled here. The functional and audibility requirements were
fulfilled as expected. The accessibility and usability requirements were not
targeted.

\paragraph{Certification}
The certification requirements assert that proofs of correctness are necessary,
which this research falls short of, but the tests and documentation available do
fulfill other certification requirements listed.

\paragraph{Authentication}
This research deeply explored authentication models and techniques for managing
access control for use in constructing voter registries. Much of this research
focused on building systems which would be reusable and composable across many
election and non-election systems; however, the result of these access control
models produced a security interface that, although working, is difficult to
interact with in a reasonable way. Inter-contract communication is difficult and
managing locks and mutexes across them is even more-so. Managing a security
interface which is entirely or mostly internal to a single contract is likely a
much safer approach to consider in most cases, although probably also a less
flexible model in the long-term. However, a majority of the most important
authentication functionalities required are provided through the underlying
blockchain infrastructure.

\paragraph{Reliability Requirements}
The underlying resiliency of the Ethereum network provides strong reliability
guarantees; however, the network is not without its issues and has seen attacks
on it over time. More recently the network has faced serious scaling issues
which have driven gas prices up and made smart contract operation an expensive
endeavour.

\paragraph{Security Requirements}
This work, by virtue of building on an Internet-based network, is accepting
risks which make any consideration or application of its results inappropriate
for use in large-scale high-risk elections. Specifically, the intrinsically
electronic and remote properties, which are inherent in all publicly-available
``off-the-shelf'' blockchain technologies, present so large an attack surface
for would-be attackers that it becomes an untenable foundation for any voting
systems being considered for use in elections where a high-risk threat model is
maintained. Correctness, security, integrity, verifiability, and efficacy are
the primary concerns of the systems designed and considered in this research;
however, it is worth noting that the privacy constraints offered by traditional
voting systems are severely loosened within the scope of this research: no
notion of receipt-freedom is assumed and privacy is only guaranteed insofar as
the pseudo-anonymity provided by the Ethereum blockchain is maintained.

It is feasible that blockchain technologies could demonstrate utility in
large-scale voting systems if incorporated using well-established and known-safe
patterns: e.g., voter verifiable paper audit trails, private networks, requiring
transactions be signed by authorized sources, using voting machines which have
been certified by a federal commission, which are being hosted in traditional
polling locations, and are leveraging the appropriate cryptographic techniques
to ensure privacy; e.g., homomorphic encryption, blind signing, and mix
networks.

\subsubsection{Non-Functional Requirements}
The non-functional requirements as described in Section~\ref{sec:requirements}
are only fulfilled insofar as this document and source code exists. Strong
efforts were not otherwise made to fulfill these requirements.

\subsection{Objectives}
Section~\ref{sec:objectives} introduced a set of objectives this research
targeted for completion. This research succeeded in exploring electoral system
design and implementation and produced several contracts demonstrating
single-winner electoral systems. However, this failed to implement a
multi-winner electoral system supporting proportional representation. STV is
often described as a complex to implement electoral system with difficult to
handle edge-cases. The finite storage and computational resources made available
by the EVM make it a poor candidate for exploration. There are other
proportional representation systems with much lower storage and execution
complexities which are probably better candidates for resource-constrained
environments like smart contracts.

This research thoroughly explored and designed many voter authentication,
registration, and access control patterns for voter registration. However, as
previously stated, inter-contract communication is difficult to manage,
especially when multiple contracts might be deferring responsibility to a single
contract managing state. This issue, combined with the resource constraints of
smart contracts, is ultimately what made further research into delegative or
liquid governance models infeasible. There are too many inter-contract
communication issues to manage when attempting to compute delegations across
contracts and there does not appear to be any clear way of designing smart
contract dependencies in a way which enabled them to be open to state changes
while still providing consistent values during sensitive contract execution
procedures like ballot tabulation or delegation analysis.

% 1. This research aims to explore various electoral systems and features, using the
% content reviewed in Section 2.1 as a basis for exploration.
% (a) Provide a range of kinds of electoral contracts using Table 2.1 and Table 2.2
% as the primary resource for electoral system and feature selection.
% i. Support single-winner elections and provide plurality and majority elec-
% toral system in fulfillment of that objective.
% A. Implement first-past-the-post to fulfill the targeted single-winner
% plurality electoral system, due mostly to the fact that it is extremely
% simple, well-understood, and widely-adopted.
% B. Implement range vote to fulfill the targeted single-winner majority
% electoral system, due to its effectiveness and simplicity.
% ii. Support multi-winner elections and provide an electoral system which
% offers proportional representation; Single transferable vote is selected as
% the electoral system implementation to fulfill both objectives due to its
% 89wide-adoption, prevalence, and effectiveness as a PR system.
% (b) Explore the design, implementation, and efficacy of various ballot types
% across the various electoral systems selected.
% 2. This research aims to explore voter authentication, registration, and access control
% patterns for managing voter registration.
% 3. This research aims to explore delegative or liquid governance models.
% 86Auditability Requirements Ethereum inherently offers a tremendously detailed
% log through its blockchain structure which provides a wide range of opportunities for
% detailed auditing and validation. Furthermore, auditing and validation functionality
% are inherent features of the blockchain. However, the auditability which Ethereum
% provides is not considered a privacy preserving feature and therefore falls short of
% the criteria presented.
% Functional Requirements A subset of the functional requirements are deemed
% relevant to this research:
%  Multi-vote functionality is targeted to be investigated and fully satisfied in all
% electoral system implementations.
% + Ensuring that “a voter’s ballot, and the act of them casting a ballot, is recorded
% and retained as expected;” is considered mostly fulfilled through intrinsic prop-
% erties of the Ethereum blockchain. Where this property falls short is when a
% voter casts a ballot, broadcasts a transaction to the network, which miners fail
% to include in any blocks. This is discussed further in Chapter 6, Discussion.
% − Maintaining voter anonymity is considered partially fulfilled through intrin-
% sic properties of the Ethereum blockchain. While it is technically possible to
% broadcast privacy-maintaining transactions, those which preserve anonymity
% on the Ethereum network, it is likely beyond the capabilities of most voting
% 87actors and would be difficult to guarantee in any meaningful way. Pseudo-
% anonymity is a better profile of the kind of anonymity whic

% \input{05-results/example}

% \blockquote{
%     Arrow assumed that social orderings will be derived, if at all, from information
%     about people's preferences. This information is, in his framework, merely
%     ordinal. It is the kind of information that is implicated in Condorcet's paradox
%     of voting, in Section 1, where each person ranks the alternatives from better to
%     worse but there is nothing beyond this about how strong anybody's preferences
%     are, or about how the preferences of one person compare in strength to those of
%     another. In confining aggregation procedures to ordinal information, Arrow
%     argued that:
%
%     [I]t seems to make no sense to add the utility of one individual, a psychic
%     magnitude in his mind, with the utility of another individual. (Arrow 1951
%     [1963]: 11)
%
%     His point was that even if people do have stronger and weaker preferences, and
%     even if the strengths of their preferences can somehow be measured and made
%     available as a basis for social decisions, nevertheless ordinal information is
%     all that matters because preferences are “interpersonally incomparable”.
%     Intuitively, what this means is that there is no saying how much more strongly
%     someone must prefer one thing to another in order to make up for the fact that
%     someone else's preference is just the other way around. Arrow saw no reason to
%     provide aggregation procedures with information about the strength of
%     preferences because he thought that they cannot put such information to
%     meaningful use.
% }

% Section: Authorization Components
% \input{05-results/sections/authorization}

% Section: Election Components
% \input{05-results/sections/election}

% Section: Delegation Components
% \input{05-results/sections/delegation}
