\acknowledgements{}

% \begin{acknowledgements}
I would like to thank first and foremost, my thesis advisor, Dr.~Cindy Norris,
for the all of the help, encouragement, advice, personal support, and patience
she has afforded me throughout this experience. I am sure we both have a few
new gray hairs to show for it. I cannot thank you enough. I would also like to
thank Dr.~James Fenwick for all of the help provided which has enabled me to
finish this work. Thank you both for all of the generosity and hospitality you
have shown me, I would not have made it if not for both of you and I am forever
grateful.

To my committee:
\begin{itemize}
  \item Dr.~Mitch Parry, thank you for all of your instruction over the years.
    Your presence has always motivated me to work harder and challenged me to
    be mindful of the things I am working on.
\item Frank Barry, you are a fountain of knowledge with more experience than
  seems possible to contain. I always find your words and our conversations
  memorable. Thank you as well for everything you have taught me over the
  years.
\item Dr.~Rahman Tashakkori, words really cannot express enough how much of an
  influence you have had on my life and how grateful I am to have met you. You
  have been like a father to me and helped me to grow in more ways than I ever
  imagined I could. I aspire to be as good a person as you one day. Thank you.
\end{itemize}

I would like to thank Google, for providing me with the opportunity to attend
the USENIX conference in San Fransisco and meet with significant members of
this field. And finally, I would like to offer a huge thank you to the NSF
S-STEM scholarship program which made my undergraduate and graduate studies
possible at Appalachian State University.
% \end{acknowledgements}
