\section{Blockchain Technologies}\label{sec:blockchain-technologies}
This research considers the utility of blockchain technologies with respect to
election systems. A blockchain is a distributed transactional database system
that tracks transactions in ever-growing linked blocks. Blockchain technologies
have been used to create immutable public ledgers for tracking currency, assets,
and rights data. The most notable technology blockchain technology in use today
is Bitcoin.

% Citation Needed
Blockchain technology exists to provide a solution to the Byzantine Generals'
Problem in a distributed computing environment.\footnotemark{} It allows parties
on an untrusted and unreliable network to build a trusted source of truth for
transaction history. Blockchains use various algorithms to score different
versions of transaction history over time to reach consensus within their
network. Blockchains might be best described as a tool used to commodify trust.

\footnotetext{
  The Byzantine Generals' Problem is a thought experiment which helps to
  illustrate some of the difficulties regarding coordination over untrusted
  networks. In short, two generals wish to coordinate an attack on an enemy
  fortress. They must attack simultaneously to succeed in taking the fortress.
  However, the general's only means of coordination is via courier, and the only
  routes available for the couriers to travel necessitate travel through the
  fortress. How do the generals coordinate their attack considering that their
  couriers might be intercepted, or worse still, replaced with dishonest spies?
}

There are interesting overlaps and parallels to be drawn from the consensus
mechanisms used in these, and other computer networks, and the consensus
mechanisms leveraged to make decisions as a group in democratic governance
systems.

% Sub-Section: Bitcoin
\input{02-background/sections/subsections/bitcoin}

% Sub-Section: Ethereum
\input{02-background/sections/subsections/ethereum}
