\section{Elections}\label{sec:elections}
Elections are perhaps the most obvious and intuitive means of allowing members
of a population to express their will and take part in their governance process.
An election is the generalized process of allowing individuals to express their
preference, typically by way of vote, as a means to come to consensus as a
group. The generalized goal of elections is to reach a consensus which
accurately and fairly reflects the preferences of the participating voters.
This, at first glance, seems like a trivial problem, and generally is in
circumstances where the number of voters and choices is small in number.
However, elections become complex as the number of actors, choices, or election
cycles increase. There are social, mathematical, and practical engineering
constraints which all voting systems are bound by, subjected to, and forced to
address.

% If we exclude singular autocratic and chaotic anarchic forms of governance then
% a system usually arises where voting is necessary.

\subsection*{Electoral Systems}
An electoral system, is the combination of rules, norms, and procedures which
define how a final result, and ultimately consensus, will be determined during
an election. Electoral systems can considered as a composition of three
components: ballot, choices, and tallying algorithm. These three components can
be woven together to produce a wide spectrum of electoral systems with varying
characteristics and properties. The choice and implementation of electoral
system has a direct and profound impact on the ways in which democratic systems
can and will operate as well as on the perceived legitimacy of the governance
model. The decisions concerning the implementation details of electoral systems
are among the most important decisions that any democratic organization will
make; the choice of design impacts all future decision making processes and
shapes the future of the governance model itself. A poorly designed electoral
system can have disastrous effects on the health and perceived legitimacy of a
democratic organization both in the immediate and long-term future. Further,
once chosen, an electoral system can be difficult to amend as political
interests respond to and solidify around the incentives presented to them which
are inherent to the electoral system chosen.\cite{electoral-handbook}

\paragraph{Choices}
A electoral system's choices are the set of options that a voting actor can
select from; they are the \emph{who} or \emph{what} being decided in an
election. The choices available may be determined by primary vote, polling,
write-in, debate, etc.\ or some other methodology or combination of
methodologies.

\subparagraph{District Magnitude}
The number of choices that will be selected as winners is of great importance in
an election. In representative democracies the measurement of seats (choices)
available is known as district magnitude. An election where the district
magnitude is one, i.e., where a single candidate or choice is to be elected or
selected, is known as a single-member district (SMD) or single-winner district.
An election where the district magnitude is greater than one, i.e., multiple
candidates are to be elected, is known as a multi-member district (MMD) or
multi-winner district.% \footnotemark{}

% \footnotetext{
%   % Much of the literature surrounding electoral systems presumes democracy via
%   % representation; this has had an influence on the language and terminology
%   % used to describe electoral systems. For example, when evaluating district
%   % magnitude terms such as ``single-member district'' and ``multi-member
%   % district'' are used --- implying that the seats available for candidacy is
%   % the metric being measured --- however, the significance of these concepts
%   % applies just the same to a vote being used to determine which pizza or
%   % pizzas should be ordered for a birthday party.
%   %
%   Much of the literature surrounding electoral systems presumes democracy via
%   representation; this has had an influence on the language and terminology used
%   to describe electoral systems. For example, a term such as ``district
%   magnitude'' implies that the seats available for candidacy is the metric being
%   measured; however, the significance of this concept applies just the same when
%   considering a vote to determine which pizza or pizzas should be ordered for a
%   birthday party.
% }

% \paragraph{Indirect Election}
% An \textbf{indirect election} is a vote where actors vote for persons who then
% elect a candidate themselves. The electoral college used in the United States
% is an example of this. When voting actors cast their vote for a particular
% candidate they're actually voting for \textbf{electors}, members of the
% electoral college who are typically aligned with the candidate's party. These
% electors are expected to vote for the candidate who wins the majority vote in a
% their state. In all but two states the electors are ``winner-take-all'', that
% is, if a candidate wins the popular vote in a state, e.g., by 50.1\%, then all
% of the electors selected for that state will be electors aligned with the
% winning candidate.
%
% \paragraph{Direct Election}
% A \textbf{direct election}, in contrast to an indirect election, is a vote
% where a voting actor's votes are cast directly for a candidate.

\paragraph{Ballot}
A ballot is the means through which voting actors express their vote. The
structure of the ballot influences exactly \emph{how} the voter can express
their preferences for a choice or choices, e.g., how many votes an individual is
able to cast. This is directly influenced by the tallying method. Ballots, in
some texts, are regarded as a process of voting; here the term is used to
describe both the medium through which a voting actor marks their choice (e.g.,
paper, punch card, or electronic machine), as well as the rules regarding how
they can mark said medium. The ballot might be thought of as the data structure
used to support the tallying algorithm.

\subparagraph{Preference Marking}
Preference marking is a ballot marking process where the electorate is given an
opportunity to rank choices: cardinally, ordinally, or by approval. This
expression of preference offers greater insights and details into the will and
desires of the electorate and can be used by the tallying method and election
officials to more optimally determine winners in an election. Preference marking
may be mandatory or optional depending on the design of the electoral system.

\paragraph{Electoral Formula}
The electoral formula is the process used to translate ballots into winning
decisions. The electoral formula is best characterized by its tallying method,
and in multi-member districts, its proportionality.

\subparagraph{Tallying Method}
The tallying method, or tallying algorithm, is closely tied to how a voter is
allowed to mark a ballot and affects how a marked ballot is ultimately counted
in the final tally of an election. Different processes of varying complexities
exist to count votes. Naturally, the process through which votes are tallied
will have a direct and significant influence on the outcome of an election.

\subparagraph{Proportionality}
Proportionality characterizes how closely votes cast translate into choices won.
The significance of proportionality becomes especially relevant as the district
magnitude increases. The closer in proportion that winning choices are to the
votes cast for them, the greater the system expresses proportionality. Analyzing
the votes cast and how they map to winning choices and ``wasted votes'' is the
easiest method to determine the proportionality of an electoral formula and is
commonly expressed as the index of disproportionality.

% \subsubsection{Conclusion}
% The choices affect \emph{who/what} you vote for, the ballot affects \emph{how}
% you express your vote, and the tallying method affects the way your expressed
% vote impacts the final results.

% \paragraph{Plurality Voting}
% A \textbf{plurality vote} system is one where

% Sub-Section: Evaluating Electoral Systems
\input{02-background/sections/subsections/electoral-system-taxonomy}

% Sub-Section: Evaluating Electoral Systems
\input{02-background/sections/subsections/evaluating-electoral-systems}

% Sub-Section: Processes, Procedures, Components, and Risks
% \input{02-background/sections/subsections/election-processes-and-prodcedures}

% Sub-Sub-Section: Voting Systems
% \input{02-background/sections/subsections/voting-systems}
