\biography{}

Nathaniel Patrick Hernandez --- born in Memphis, Tennessee, to Alison and Juan
Hernandez --- developed a passion for technology and software at a young age
and has been passionately writing software and exploring the field of computer
science ever since. In 2012 Nathan earned his Associate of Science from Coastal
Carolina Community College. The next year, with barely the wherewithal to
attend a single semester, he began his Bachelor of Science at Appalachian State
University. Nathan was fortunate to have been noticed by the faculty of The
Department of Computer Science there and presented with opportunities to work
with faculty members in a variety of ways.

Dr.~Rahman Tashakkori in particular played a significant role in Nathan's
undergraduate degree, academic career, and personal life --- investing
significant amounts of time and energy which came in the shape of mentorship,
engaging academic problems, personal challenges, and friendship --- helping
Nathan to grow personally, academically, and eventually providing the
encouragement to pursue a Master's degree. Throughout Nathan's academic career
Dr.~Tashakkori presented him with scholarship and research opportunities;
allowing him, along with a team of other hand-picked students, to conduct
research, built software and hardware systems, publish results, and present
findings on the beehive monitoring and analytics systems they built together.
This research served as the foundation for Nathan's undergraduate thesis which
enabled him to earn his Bachelor of Science.

Outside of academia, Nathan spent just under a year interning with IBM's jStart
team, a small group within IBM's Emerging Technologies department responsible
for prototyping systems for clients which leveraged new and promising
technologies. Nathan spent a majority of his time there immersing himself in
the field of big-data analytics: exploring Apache Kafka, analyzing client data,
generating insights, and building real-time data-processing pipelines. Having a
strong interest in cybersecurity and cryptography, Nathan also spent a summer
in San Fransisco, California, interning at UnifyID, a startup whose goal is to
build advanced security, authentication, and password management solutions.
While there Nathan worked on building important components of UnifyID's Google
Chrome extension for password management and participated in launching their
private beta. A few months after the end of his internship UnifyID went on to
win runner-ups in the 2016 TechCrunch Disrupt Battlfield.

% and present
% results, and explore challenging unique ideas which eventually resulted in

% Your biography is limited to one page and must contain
% \begin{enumerate}
%     \normalbaselines{}
% \item Full name
% \item Date and place of birth
% \item Every degree you've earned, including this one, and where you earned it
%     from.
% \end{enumerate}
% Mostly, that information is to narrow down which John Smith wrote that
% dissertation on the mating habits of sea cucumbers.  Sexy!
%
% You may also include
% \begin{enumerate}
%     \item Any awards you've won related to your discipline since your
%         undergraduate degree.
%     \item Any fellowships you've held
%     \item Anything you've published (papers, books, book chapters).  Don't be
%         afraid to cite it here, so that the full bibliographic record of your
%         article appears in the bibliography!
%     \item Where your next job will be, if you know
% \end{enumerate}


% VITA
% David John Cholmondeley II was born in Florence, Italy, to David and Shelby
% Cholmondeley. He graduated from Andover Academy in Massachusetts in June 1992.
% The following autumn, he entered Manchester University to study History, and in
% June 1995 he was awarded the Bachelor of Arts degree. In the fall of 1995, he
% accepted a research assistantship in History at Appalachian State University
% and began study toward a Master of Arts degree. The M.A. was awarded in June
% 1997. In September 1997, Mr. Cholmondeley commenced work toward his Ph.D. in
% International Trade at Georgetown University.
%
% Mr. Cholmondeley is a member of Phi Kappa Phi and Alpha Epsilon Lambda, and
% remains active in scouting as a troop leader. He resides in Washington, D.C.
% with his wife and four children.
